---
title: "Set-Valued Policy Learning"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# 1. Introduction 

We implement set-valued policy learning as proposed in [1], where 
the learning algorithm outputs a set of candidate treatments rather than a single 
decision. This approach is designed to provide formal coverage guarantees—ensuring 
that the optimal treatment are included in set-valued policies.

This repository implements the two methods presented in the paper:
* (i) *Greatest lower bound* (GLB): Based on upper and lower confidence bounds 
on conditional outcomes.
* (ii) *conformal set-valued policy learning*: Based on conformal prediction under 
label noise.

[1] Anonymous Authors. (2026). Set-Valued Policy Learning. 

# 2. Getting started 

This section demonstrates a basic example of how to use the `setValuedPolicyLearning` package. 
We begin by generating a synthetic data set and applying the main function, 
`learn_set_valued_policies()`, to learn an set-valued policies for different 
confidence levels.

## 2.1. Setting environment 

You can install the development version from your local source:
```{r,eval=FALSE}
devtools::install_local(
    "path/to/downloaded_file.tar.gz",
    dependencies = TRUE)
```

Load required packages 
```{r setup}
library(setValuedPolicyLearning)
library(SuperLearner)
library(grf)
library(dplyr)
library(tidyr)
library(ggplot2)
```

## 2.2. Synthetic data generation

We generate synthetic observational data using the built-in `generate_data()` 
function. This function also produces the complete data structure (which is 
typically unavailable in real-world applications and used here for evaluation 
purposes only). 

```{r synthetic data generation}
# Set parameters  
n <- 6000 # number of observations 
ncov <- 4 # number of covariates
type <- "normal" # type of synthetic scenario (either "normal" or "complex)
is_RCT <- FALSE 
seed <- 2026

# Generate training data
# ---------------------------------------------------------------
# Reminder:
# - Ensure categorical variables are one-hot encoded 
#   (dummy variables) prior to inclusion. 
# ---------------------------------------------------------------

exp <- generate_data(n, ncov = ncov, type=type, is_RCT=is_RCT, seed = seed)
X <- exp[[1]] %>% select(starts_with("X")) # extract covariates 
A <- exp[[1]]$A # extract treatment factor 
Y <- exp[[1]]$Y # extract outcome 

# Generate test data
exp_test <- generate_data(500, ncov = ncov, type=type, is_RCT=is_RCT, seed = seed)
X_test <- exp_test[[1]] %>% select(starts_with("X")) # extract covariates 
A_test <- exp_test[[1]]$A # extract treatment factor 
Y_test <- exp_test[[1]]$Y # extract outcome 
```

## Generate set-valued policies 

First pre-specify the function inputs. 
```{r}
# Confidence levels to test 
# Values must be included in [0,1] 
alphas = seq(0,0.5,0.05)

# SuperLearner library used for estimating nuisance functions
# You can customize this list. The default includes:
# - SL.mean: simple mean predictor
# - SL.glm: generalized linear model
# - SL.ranger: random forest
# - SL.xgboost: gradient boosting
SL.library_nuissance <- c("SL.mean", "SL.glm", "SL.ranger", "SL.xgboost")

# Randomness levels for conformal set-valued policy learning 
# Values must be included in [0,1] 
random_rate <- c(0,0.2,0.4,0.6)

# Noisy label generation algorithms (with polle package)
# Customize the learner by selecting/adding elements to the lists below:
# - type: Kind of learner to be used. 
#         Options: "drql" (Doubly Robust), "ql" (Q-learning), "plt" (Policy Tree)
# - q_func: ML model for the Q-model.
#           Options: q_glm, q_rf (Random Forest), q_sl (SuperLearner), 
#                    q_xgboost, q_glmnet
# - sl_library: Ensemble library (only required when q_func = q_sl).
#               Specify a single package or a character vector of several.
label_generation = list(list(type = "drql", q_func = "q_glm"), 
                         list(type = "drql", q_func = "q_sl", sl_library = "SL.xgboost"))
```

Run the algorithm to learn set-valued policies: 
```{r, eval=FALSE}
results <- learn_set_valued_policies(X = X, A = A, Y = Y, X_test = X_test, 
                                     A_test = A_test, Y_test = Y_test, 
                                     random_rate = random_rate, 
                                     alphas = alphas, 
                                     label_generation = label_generation, 
                                     SL.library.nuisance = SL.library_nuissance)
```
Extract important features and learnt set-valued policies: 
```{r, eval=FALSE}
# Extract important features 
SL.out <- results[["SL.out"]]

# Extract set-valued policies (SVP)
svp <- results[["confidence_sets"]]

# 1. Greatest Lower Bound (GLB) Policies
# Learned via grf::regression_forest
svp_GLB <- svp$GLB
# View available confidence levels for GLB
print("confidence levels: ")
print(svp_GLB %>% names())

# 2. Conformal Prediction Policies for different random_rate values
svp_C <- svp$conformal
# View randomness levels for a specific confidence level (e.g., alpha = 0.1)
print("randomness levels: ")
print(svp_C$`alpha=0.1` %>% names())
```

Evaluate set-valued policies at confidence level $\alpha=0.1$
```{r, eval=FALSE}
# uniform set-policy value of GLB 
n_test <- 10 # number of random policies sampled
value_GLB <- set_policy_value(svp_GLB$`alpha=0.1`, ab = SL.out$ab,
                 test= SL.out$df_new, levels=levels(A), n_test=n_test,
                 covariates = SL.out$feature_names[[1]],
                 treatment_name = SL.out$feature_names[[2]],
                 outcome_name = SL.out$feature_names[[3]],
                 mod_y=SL.out$QAW.reg.train,
                 mod_ps = SL.out$g.reg.train)
cardinality_GLB <- width(pred_set = svp_GLB$`alpha=0.1`, levels = levels(A))

# uniform set policy value for conformal policies
value_conformal <- sapply(svp_C$`alpha=0.1`, function(policy) {
  set_policy_value(
    policy, n_test= n_test,
    ab = SL.out$ab,
    test = SL.out$df_new, 
    levels = levels(A), 
    covariates = SL.out$feature_names[[1]],
    treatment_name = SL.out$feature_names[[2]],
    outcome_name = SL.out$feature_names[[3]],
    mod_y = SL.out$QAW.reg.train,
    mod_ps = SL.out$g.reg.train)
})
cardinality_C <-  sapply(svp_C$`alpha=0.1`, function(policy) {
  width(pred_set = policy, levels = levels(A))})


# Compare both set-valued policies 
set_policy_value <- colMeans(cbind(value_conformal, value_GLB))
print("Mean set policy values:")
print(set_policy_value)

# Compare both mean cardinalities
cardinalities <- c(cardinality_C, cardinality_GLB)
print("Mean set policy values:")
print(cardinalities)
```